An Integrated Framework for Robust Estimation, Prediction and Control

### 2019-12-02 main.tex
Update notations

\paragraph{Structured dynamics}
We consider a system with continuous state space $\Real^p$ and dynamics in the form:

\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t)+B_u u(t) + B_\omega \omega(t),\;t\geq0,
\end{equation}
\todo[inline]{EL: merge notations of the system with and without command $u$}
where $\theta$ belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and $\omega$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.

\paragraph{Robust objective}

We wish to find a sequence of commands $\pi=(u(t))_{t\geq 0}$ that maximises the robust control objective $v^r$:
\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}

@@

This involves the trilemma of confidence intervals, where one of three things must be true:
\begin{itemize}
    \item $A(\theta)$ is in $\cC_\delta$
    \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
    \item Our model is wrong
\end{itemize}

@@

>>>>

\paragraph{Structured dynamics}
We consider a system with dynamics in the form:

\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t)+B_u u(t) + B_\omega \omega(t),\;t\geq0,
\end{equation}
with a state $x\in\Real^p$, control $u\in\Real^m$, parameter $\theta$ that belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and where $\omega\in\Real^q$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.
\todo[inline]{EL: merge notations of the system with and without command $u$}

\paragraph{Objective}

We wish to find a sequence of commands $\pi=(u_t)_{t\geq 0}$ that maximises a cumulative objective $V^\pi$:
\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}

\todo[inline]{EL: the prediction is done in continuous time and the control in discrete time. How to handle the change in notations?}

\begin{equation}
\max_\pi V^\pi
\end{equation}
where
\begin{equation}
\label{eq:optimal-control}
V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \eqref{eq:dynamics}, u_t = \pi(x_t)\right]
\end{equation}
and $r$ is a bounded reward function.

@@

This involves the trilemma of confidence intervals, where one of three things must be true:
\begin{enumerate}
    \item $A(\theta)$ is in $\cC_\delta$
    \item We got data that was very ($\leq\delta$) unlikely under all possible values $A(\theta)$
    \item Our model is wrong
\end{enumerate}

@@

The \textbf{robust control} objective $v^r$:
\todo[inline]{EL: since the interval dynamics will be deterministic, use open-loop policies, ie sequences of actions $\mathbf{u}$ instead of closed-loop policies $\pi$}
